% !Mode:: "TeX:UTF-8"

\begin{Eabstract}{mysql}{java}{mysql}{java}{mysql}
Database, operating system and compiler and called the three systems, can be said that the cornerstone of the entire computer software. Which is closer to the application layer database, is a lot of business support. This field after decades of development,
There are new developments. From the beginning of the hierarchy database and relational database, to the recent hot Nosql database, and then to the recent Google Spanner and F1 as the representative of the NewSql database.

In the Internet age, the storage and access of massive data becomes the bottleneck of system design and use. For mass data processing,
King, divided into two types: online transaction processing (OLTP) and online analytical processing (OLAP).

Relational database is based on the relational model of the database, which by means of aggregation algebra and other mathematical concepts and methods to deal with the database
data. Which is the most popular mysql, mysql is an open source relational database, the advantage lies in the open source code, any business and individuals can according to their own needs to modify the source code mysql.

NoSQL database, called Not Only SQL, meaning that when the relational database is used when the relational database, not applicable
There is no need to use relational database is not necessary, you can consider the use of more appropriate data storage.

Oracle, mysql and other traditional relational database is very mature and has been large-scale commercial, why use NoSQL database? mainly
With the development of the Internet, the amount of data is growing, the performance requirements are getting higher and higher, the traditional database of congenital defects, namely stand-alone (single
Library) performance bottlenecks, and difficult to expand. This is a stand-alone single library bottleneck, but difficult to expand, naturally unable to meet the growing mass of data storage
And its performance requirements, so there will be a variety of different NoSQL products.

Although in the cloud computing era, the traditional database there are congenital defects, but NoSQL database can not be replaced, NoSQL can only
For the traditional data supplement can not be replaced, so to avoid the shortcomings of traditional databases is the current era of large data must be resolved.

In order to solve these problems, such as mysql and other relational database, this article describes how to design and implement a compatible mysql protocol distributed database. He can automatically find the distributed database cluster nodes,
Automatically allocate data to support massive data storage. Taking into account the increasingly important security of the database, from time to time the occurrence of database administrators or other attackers malicious changes in the database data,
So the database developed by the database from the bottom of the database to join the audit function.

The main work of this paper is as follows:

Based on the realization of java language compatible mysql communication protocol database;

The realization of the database cluster, to achieve the database of high availability, scalability, load balancing and other characteristics;

From the bottom of the database to consider the database security, joined the data audit and other features.
\end{Eabstract}
